\section{Project Summary} 
\label{sec:project_summary}

 

\subsection{Project Summarization}
 
Bike sharing systems are gaining immense popularity as an alternative or complementary mode of urban transport. Bike sharing can provide an alternative to traditional modes of transport or, more likely a complementary service for solving the ”last mile problem” of getting from a public transportation stop to the final destination. The whole project is aimed at shedding light on how well the bike sharing model is working in the LA metropolitan area.  

\subsection{What we did during the course of the project?}

We worked with the data provided by Kaggle and the open source data from Metro Bike Share. The initial structure of the data was in CSV format, from which after primary data cleaning in python, we converted it to GeoJson format. We divided our tasks according to according to Shneiderman Task taxonomy which also conforms to our project goal. Then we proceeded to make the visualization. Our work was to create a geographic map detailing every station according to their longitude and latitude; along with the numbers of rentals from each of those stations. We also added a histogram for every month from July of 2016 to September of 2018, which we used for the selection of the rentals in that particular timeframe. 


\subsection{What contributions are presented in this milestone?}
 
In this milestone, our major focus was towards the evaluation of our visualization. So, for this purpose, we presented our visualization to a group of six people with some open-ended and close-ended questions. We also made a comparison of our visualization with another visualization with a somewhat equivalent goal. And in the end, we made a presentation in front of our class which was entirely comprised of people from visualization background and collected feedback.

\subsection{What contributions were presented in the previous milestones?}

In the previous milestone, our work was focus towards the collection of the data and making the visualization design. Milestone 1 was about the proposal of the project; in milestone 2 we worked on data and task abstraction and how to proceed with the preliminary design. In next milestone, we created our initial skeleton of the geographical map and in milestone 4 we finetuned the map, along with the tooltips and created the histogram for data filtering.


