\section{Schedule} 
\label{sec:schedule}

For the second project milestone, we started off by trying to complete the proposed goals that were listed in the first project milestone. Following are those proposed goals:
\begin{enumerate}
    \item Finalize on the dataset for visualization
    \item Perform data cleansing and abstractions, categorizing them in the order in which they are mapped
    \item Discuss and agree on detailed work division for the project
    \item Perform initial visualization sketches
    \item Decide on the feasibility of current visualization ideas and add/remove as required
\end{enumerate}

Out of the five proposed goals, all goals except the second goal were completed. We were able to finalize on a dataset to be used for the project. There are a lot of open-source bike-sharing datasets available to choose from and most of them have the same set of attributes. We decided to go with the BikeShare Metro Los Angeles dataset.
We also discussed and agreed upon a detailed work division for the project. This task cannot be checked off as completed finished right now because we are still flexible about our task division. But what we have done is, agreed upon each member being the go-to person for a specific topic or application no matter who might be working on it. This results in every member being a spokesperson for one(or more) sections but still working together as a team.
Initial visualization sketches about what our visualization might look like at the end of the project were also made. Finally, we discussed and decided on the feasibility of our current visualization ideas. Through this process, we added the visualization which we eventually selected as the primary visualization for our project. Also, we decided that mapping the weather data should be kept as a future optional milestone and be done only if we had time.

We were not able to perform cleansing of our data and also did not categorize them in the order in which they are mapped. The primary reason for our inability to complete this goal was our lack for foresight when we planned for the second milestone. Initially, we had assumed that we would be able to start with the data cleansing and management task for the second milestone but picking the final visualization took more time than expected for us. This was a challenge for us during the initial stages of research. We went through a lot of research materials and also consulted various visualization students regarding our ideas. After careful consideration, we came to an agreed conclusion.

In addition to this, deciding on the dataset and on the feasibility of our visualization from PM1 took more time than initially planned. Our plan to start writing code and working with data only after deciding on a final visualization was a bad choice since that in part led us to miss goal 2 in our milestone. We could have started working with data and performing initial cleaning and formatting to it since that is not dependent on our final choice of visualization. We will make sure to think about these scenarios and prevent them from happening in the remaining milestones.

\begin{table}[h]
%% Table captions on top in journal version
 \caption{Project Milestones}\vspace{1ex} % the \vspace adds some space after the top caption
 \label{tab:milestones}
 \scriptsize
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
   \begin{tabular}{p{2cm}|p{6cm}}
     Milestone & Description (\%)\\
   \hline
     PM3 & Perform initial data cleansing and formatting to make input reads more streamlined\\
         & Create basic geographic visualizations using maps of the desired location\\
         & First visualization mapping the busiest locations in the city complete\\
         & Initial work on panning and zooming started\\
     PM4 & Right panel of time frame histogram designed and working\\
         & Linking the left and right visualization complete\\
	     & Refined the interactions within a visualization\\
	     & Initial stages of evaluation started\\
	     & Started preparations for the class presentation\\
     PM5 & Evaluation process completed\\
         & Revised data analysis and visualization tuning because on evaluation feedback\\
         & Class presentation and report submission completed\\
   \end{tabular}
\end{table}
